---
title: "02_Clustering"
author: "Lukas Weixler"
date: "26 7 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, sampling, apcluster, data.table, dtw, tictoc, reticulate, ggdendro, ggfortify, reshape2, purrr)

py_config()

py_install('pandas')

source_python('helperCode/add.py')
```

```{r}
load("~/data/feats_normed.RData")
load("~/data/SPDat_reduced_all.RData")
load("~/data/feat_importance_clustered.RData")

available_feats_normed <- feats_normed
```



# Extract ts length from data
```{r}

len_df <- function(elm){
  out <- elm$n 
  return(out)
}


lens <- lapply(spdat_reduced_all, len_df)


len_df <- data.frame(matrix(unlist(lens), nrow = length(lens), byrow = T))

len_df <- len_df %>% rename(length_ts = matrix.unlist.lens...nrow...length.lens...byrow...T.)
```




# Assign counter variable for length occurences
```{r}
helper_df <- len_df %>% 
  
  # Count occurences of a length
  group_by(length_ts) %>% 
  tally() #%>% 
  
  # Join to get the correct order for strata back
  samp_df <- helper_df %>% left_join(len_df)
```


# Prepare dataset to only sample from frequently occuring lengths
```{r}


# Sample 10% of occurence if n is larger than 10
sampsizes <- ifelse(helper_df$n >= 10,round(0.1*helper_df$n),1)
```


# Extract strata based on proposed sampsizes above
```{r}

set.seed(2021)
all_insamp_indx <- strata(samp_df, stratanames = c("length_ts"), size = sampsizes, method = 'srswor')
```

### Index Dataframe to be able to reorder all features to their Time Series
```{r}
all_indxs <- tibble(ID_unit = c(seq(1:nrow(samp_df))))
```

```{r}
all_outsamp_indxs <- all_indxs %>% anti_join(all_insamp_indx %>% select(ID_unit))
```


# Extract from original df via indexno, also get non sampled feats via anti join
```{r}
all_samped_units <- available_feats_normed[all_insamp_indx$ID_unit,] 
```

```{r, echo=F}
all_non_samped_units <- available_feats_normed[all_outsamp_indxs$ID_unit,]
```


### Clustering

```{r}
prp <- py_affinity_propagation(all_samped_units)
```


### Predicting nonsampled units

prp 1 contains the model
```{r}
preds <- py_affinity_predictor(prp[[1]], all_non_samped_units)
```



```{r}
nonsamped_preds <- all_non_samped_units %>% mutate(cls_label = preds, insamp = rep(0, nrow(all_non_samped_units))) %>% mutate(cls_center = 0)
```

```{r}
samped_labs <- all_samped_units %>% mutate(cls_label = prp[[2]], insamp = rep(1, nrow(all_samped_units))) %>% mutate(cls_center = 0)
```

### Label representatives with 1 for cls center
```{r}
samped_labs[prp[[3]],]$cls_center <- 1
```


### Bind nonsampled and sampled, including sample and cluster information

```{r}
all_data_labelled <- samped_labs %>% 
  
  # add ID unit in original TS List to sampled lables
  mutate(ID_unit = all_insamp_indx$ID_unit) %>% 
  
  # Add ID unit to non sampled predictions before rowbinding
  bind_rows(nonsamped_preds %>% mutate(ID_unit = all_outsamp_indxs$ID_unit)) 
```


### Plotting count per cluster
```{r}
all_data_labelled %>% filter(insamp==1) %>% ggplot(aes(cls_label))+geom_bar()+ggtitle('Number of TS per cluster over sampled Data')

all_data_labelled %>% ggplot(aes(cls_label))+geom_bar()+ggtitle('Number of TS per cluster over all Data')
```


### Importance of sampled units
```{r}
#cls_importances



feat_importance_insamp <- lapply(0:39, function(i){py_xgbooster(feat_importance_prep_insamp %>% mutate(cls_label = ifelse(cls_label == i, 1, 0)))})

```



```{r, fig.height=10, fig.width=15}

cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

importancePlottr <- function(cls_elm, clsno, colours = c("1" = "#62879c", "2" = "#FF9900", "3" = "#CCFF00", "4" = "#fff478", "6" = "#00FF66", "7"="#00FFFF", "8"="#FF0000", "9"="#3300FF", "5"="#CC00FF", "0"="#000000")){
  
  

plts <- cls_elm  %>% arrange(desc(importances)) %>% head(15) %>% 
  left_join(feat_importance_clustered %>% select(-importances))%>%
  mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances), fill=cls))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_fill_manual(values = colours)+
  ggtitle(paste('CLS ', clsno))+coord_flip()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=15),
        plot.title = element_text(size=20) )

return(plts)
}
```



# Plotting feature importance per cluster

```{r, echo=F, message=F}
plts <- map2(feat_importance_insamp, c(seq(0,39)), importancePlottr)
```




### Get information on most important features for each cluster

```{r}

# Run over all 36 clusters
all_plts <- lapply(1:40,function(j){
print(j)
# Grab importances of first cluster, join with full df to have feature cls
most_im_five <- feat_importance_insamp[[j]] %>% left_join(feat_importance_clustered %>% select(-importances)) %>% arrange(desc(importances)) %>% head(5) %>% select(names)



# Get overall mean of most important features for all values
all_vals <- all_data_labelled %>% filter(insamp==1) %>% select(most_im_five$names) %>%   summarise_all(mean) %>% melt(variable.name=c('varname'), value.name = c('overall_mean')) 


# Get overall mean of most important features for cluster values
cls_vals <- all_data_labelled %>% filter(insamp==1&cls_label == j-1) %>% select(most_im_five$names) %>% summarise_all(mean) %>% reshape2::melt(variable.name=c('varname'), value.name = c('cluster_mean')) 

# Get singular values of most important features for representative time series
repr_val <- all_data_labelled %>% filter(cls_center==1&cls_label == j-1) %>% select(most_im_five$names) %>% melt(variable.name=c('varname'), value.name = c('represent_TSfeature')) 


# Join values together
means_comp<-all_vals %>% inner_join(cls_vals, by=c('varname')) %>% inner_join(repr_val,by=c('varname')) #%>% mutate(repr = as_factor(c(0,0,1)))


# Make plot for each feature individually
out <- lapply(1:5,function(i){means_comp %>% 
    reshape2::melt(variable.name=c('group')) %>% 
    
    # Pick respective feature via filter
    filter(varname== most_im_five$names[i]) %>% 
    
    # Define column for who is representative
    mutate(representative=as_factor(c(F,F,T))) %>% 
    
    # Make Plot
    ggplot(aes(value,representative))+
    geom_line(aes(group=representative))+
    geom_point(aes(color=group, size = 5))+
    theme(axis.text.y=element_text(size=10),
          axis.text.x=element_text(size=10), 
          text = element_text(size=10), 
          legend.position = "none",
          )+
    # Title for orientation based on cls and varname
    ggtitle(paste('CLS ',j-1 , " variable: ", gsub("_", ".", most_im_five$names[i])))})

return(out)})





```



### Visualize cls centers

```{r}
# If ts is in affinity sample, then add to list
sp_cls <- c()

for (i in 1:length(spdat_reduced_all)){
  if(spdat_reduced_all[[i]]$cls_information$cls_center == 1 ){
  sp_cls[[length(sp_cls)+1]] <- spdat_reduced_all[[i]]}}
```


```{r, fig.width=10}
serieslst <- map2(sp_cls, c(seq(0:39)), function(lstelm, i){lstelm$Series %>% autoplot()+ggtitle(paste('Center of cls', i-1))+
      theme(
    axis.text.x = element_text(angle = 90, size=20),
    title = element_text(size=25))})
```