---
title: "AffinityPropagation"
author: "Lukas Weixler"
date: "26 4 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
pacman::p_load(tidyverse, sampling, apcluster, data.table, dtw, tictoc, reticulate, ggdendro, ggfortify, reshape2, purrr)

py_config()

py_install('pandas')

source_python('helperCode/add.py')
```



# Extract ts length from data
```{r}

len_df <- function(elm){
  out <- elm$n 
  return(out)
}


lens <- lapply(spdat_reduced_all, len_df)


len_df <- data.frame(matrix(unlist(lens), nrow = length(lens), byrow = T))

len_df <- len_df %>% rename(length_ts = matrix.unlist.lens...nrow...length.lens...byrow...T.)
```




# Assign counter variable for length occurences
```{r}
helper_df <- len_df %>% 
  
  # Count occurences of a length
  group_by(length_ts) %>% 
  tally() #%>% 
  
  # Join to get the correct order for strata back
  samp_df <- helper_df %>% left_join(len_df)
```


# Prepare dataset to only sample from frequently occuring lengths
```{r}


# Sample 10% of occurence if n is larger than 10
sampsizes <- ifelse(helper_df$n >= 10,round(0.1*helper_df$n),1)
```


# Extract strata based on proposed sampsizes above
```{r}

set.seed(2021)
all_insamp_indx <- strata(samp_df, stratanames = c("length_ts"), size = sampsizes, method = 'srswor')
```

### Index Dataframe to be able to reorder all features to their Time Series
```{r}
all_indxs <- tibble(ID_unit = c(seq(1:nrow(samp_df))))
```

```{r}
all_outsamp_indxs <- all_indxs %>% anti_join(all_insamp_indx %>% select(ID_unit))
```

```{r}
available_feats_normed <- data_to_reduce
```


# Extract from original df via indexno, also get non sampled feats via anti join
```{r}
all_samped_units <- available_feats_normed[all_insamp_indx$ID_unit,] 
```

```{r, echo=F}
all_non_samped_units <- available_feats_normed[all_outsamp_indxs$ID_unit,]
```


### Clustering

```{r}
prp <- py_affinity_propagation(all_samped_units)
```


### Predicting nonsampled units

prp 1 contains the model
```{r}
preds <- py_affinity_predictor(prp[[1]], all_non_samped_units)
```



```{r}
nonsamped_preds <- all_non_samped_units %>% mutate(cls_label = preds, insamp = rep(0, nrow(all_non_samped_units))) %>% mutate(cls_center = 0)
```

```{r}
samped_labs <- all_samped_units %>% mutate(cls_label = prp[[2]], insamp = rep(1, nrow(all_samped_units))) %>% mutate(cls_center = 0)
```
### Label representatives with 1 for cls center
```{r}
samped_labs[prp[[3]],]$cls_center <- 1
```





### Bind nonsampled and sampled, including sample and cluster information

```{r}
all_data_labelled <- samped_labs %>% 
  
  # add ID unit in original TS List to sampled lables
  mutate(ID_unit = all_insamp_indx$ID_unit) %>% 
  
  # Add ID unit to non sampled predictions before rowbinding
  bind_rows(nonsamped_preds %>% mutate(ID_unit = all_outsamp_indxs$ID_unit)) 
```


### Plotting count per cluster
```{r}
all_data_labelled %>% filter(insamp==1) %>% ggplot(aes(cls_label))+geom_bar()+ggtitle('Number of TS per cluster over sampled Data')

all_data_labelled %>% ggplot(aes(cls_label))+geom_bar()+ggtitle('Number of TS per cluster over all Data')
```







### Visualize Feature importance, obtained from XGBoost in Python

```{r}
feat_importance_prep <- all_data_labelled[,c(seq(1,269))] %>% mutate(cls_label = as.factor(cls_label))
```

```{r}
feat_importance <- py_xgbooster(feat_importance_prep)
```


```{r}
feat_importance_clustered <- feat_importance %>% inner_join(feat_importance_clustered %>% select(-importances)) 
```





```{r, fig.height=35, fig.width=15}
feat_importance_clustered  %>% mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances)))+
  geom_bar(stat='identity', position = 'dodge')+
  theme(axis.title.y=element_blank(),  axis.text.y=element_text(size=10))+coord_flip()
```


```{r, fig.height=35, fig.width=15}

my_colrs <- c("1" = "#999999", "2" = "#E69F00", "3" = "#56B4E9", "4" = "#009E73", "6" = "#F0E442", "7"="#0072B2", "8"="#D55E00", "9"="#CC79A7", "5"="#87FF33", "0"="black")


feat_importance_clustered  %>% mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances), fill=cls))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_fill_manual(values = my_colrs)+
  theme(axis.title.y=element_blank(),  axis.text.y=element_text(size=10))+coord_flip()
```


### Compare above plot with feature importance for insamp ts


```{r}
feat_importance_prep_insamp <- all_data_labelled %>% filter(insamp == 1) %>% select(-c(270,271,272)) %>% mutate(cls_label = as.factor(cls_label))
```

```{r}
feat_importance_insamp <- py_xgbooster(feat_importance_prep_insamp)
```


```{r}
feat_importance_insamp_clustered <- feat_importance_insamp %>% inner_join(feat_importance_clustered %>% select(-importances)) 
```





```{r, fig.height=35, fig.width=15}
feat_importance_insamp_clustered  %>% mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances)))+
  geom_bar(stat='identity', position = 'dodge')+
  theme(axis.title.y=element_blank(),  axis.text.y=element_text(size=10))+coord_flip()
```




```{r, fig.height=35, fig.width=15}
my_colrs <- c("1" = "#999999", "2" = "#E69F00", "3" = "#56B4E9", "4" = "#009E73", "6" = "#F0E442", "7"="#0072B2", "8"="#D55E00", "9"="#CC79A7", "5"="#87FF33", "0"="black")


feat_importance_insamp_clustered  %>% mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances), fill=cls))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_fill_manual(values = my_colrs)+
  theme(axis.title.y=element_blank(),  axis.text.y=element_text(size=10))+coord_flip()
```

### Compare in scatterplt
```{r}
# Append handlabeled feat clusters via join
importance_cmp <- feat_importance_clustered %>% inner_join(feat_importance_insamp_clustered, by='names')
```



```{r}
ggplot(importance_cmp, aes(x=importances.x, y=importances.y))+geom_point()
```
```{r}
mod <- lm(importances.y~importances.x, data=importance_cmp)

summary(mod)
```


```{r}
#cls_importances



feat_importance_insamp <- lapply(0:39, function(i){py_xgbooster(feat_importance_prep_insamp %>% mutate(cls_label = ifelse(cls_label == i, 1, 0)))})

```

```{r}
lab <- all_data_labelled[all_data_labelled$cls_center & all_data_labelled$cls_label == 0, ID_unit]
```

```{r}
autoplot(spdat_reduced_all[[lab]]$Series)
```





```{r, fig.height=10, fig.width=15}

cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

importancePlottr <- function(cls_elm, clsno, colours = c("1" = "#62879c", "2" = "#FF9900", "3" = "#CCFF00", "4" = "#fff478", "6" = "#00FF66", "7"="#00FFFF", "8"="#FF0000", "9"="#3300FF", "5"="#CC00FF", "0"="#000000")){
  
  

plts <- cls_elm  %>% arrange(desc(importances)) %>% head(15) %>% 
  left_join(feat_importance_clustered %>% select(-importances))%>%
  mutate(cls=as.factor(cls)) %>% 
  ggplot(aes(y = importances, x = reorder(names, importances), fill=cls))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_fill_manual(values = colours)+
  ggtitle(paste('CLS ', clsno))+coord_flip()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=15),
        plot.title = element_text(size=20) )

return(plts)
}
```





```{r, echo=F, message=F}
plts <- map2(feat_importance_insamp, c(seq(0,39)), importancePlottr)
```




```{r, fig.height=60, fig.width=60}
library(gridExtra)
n <- length(plts)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(plts, ncol=nCol))
```







### Get information on most important features for each cluster

```{r}

# Run over all 36 clusters
all_plts <- lapply(1:40,function(j){
print(j)
# Grab importances of first cluster, join with full df to have feature cls
most_im_five <- feat_importance_insamp[[j]] %>% left_join(feat_importance_clustered %>% select(-importances)) %>% arrange(desc(importances)) %>% head(5) %>% select(names)



# Get overall mean of most important features for all values
all_vals <- all_data_labelled %>% filter(insamp==1) %>% select(most_im_five$names) %>%   summarise_all(mean) %>% melt(variable.name=c('varname'), value.name = c('overall_mean')) 


# Get overall mean of most important features for cluster values
cls_vals <- all_data_labelled %>% filter(insamp==1&cls_label == j-1) %>% select(most_im_five$names) %>% summarise_all(mean) %>% reshape2::melt(variable.name=c('varname'), value.name = c('cluster_mean')) 

# Get singular values of most important features for representative time series
repr_val <- all_data_labelled %>% filter(cls_center==1&cls_label == j-1) %>% select(most_im_five$names) %>% melt(variable.name=c('varname'), value.name = c('represent_TSfeature')) 


# Join values together
means_comp<-all_vals %>% inner_join(cls_vals, by=c('varname')) %>% inner_join(repr_val,by=c('varname')) #%>% mutate(repr = as_factor(c(0,0,1)))


# Make plot for each feature individually
out <- lapply(1:5,function(i){means_comp %>% 
    reshape2::melt(variable.name=c('group')) %>% 
    
    # Pick respective feature via filter
    filter(varname== most_im_five$names[i]) %>% 
    
    # Define column for who is representative
    mutate(representative=as_factor(c(F,F,T))) %>% 
    
    # Make Plot
    ggplot(aes(value,representative))+
    geom_line(aes(group=representative))+
    geom_point(aes(color=group, size = 5))+
    theme(axis.text.y=element_text(size=10),
          axis.text.x=element_text(size=10), 
          text = element_text(size=10), 
          legend.position = "none",
          )+
    # Title for orientation based on cls and varname
    ggtitle(paste('CLS ',j-1 , " variable: ", gsub("_", ".", most_im_five$names[i])))})

return(out)})





```


#### Approach 2

```{r}

# Run over all 36 clusters
all_plts <- lapply(1:40,function(j){
print(j)
# Grab importances of first cluster, join with full df to have feature cls
most_im_five <- feat_importance_insamp[[j]] %>% left_join(feat_importance_clustered %>% select(-importances)) %>% arrange(desc(importances)) %>% head(5) %>% select(names)



# Get overall mean of most important features for all values
all_vals <- all_data_labelled %>% filter(insamp==1) %>% select(most_im_five$names) %>%   summarise_all(mean) %>% melt(variable.name=c('varname'), value.name = c('overall_mean')) 


# Get overall mean of most important features for cluster values
cls_vals <- all_data_labelled %>% filter(insamp==1&cls_label == j-1) %>% select(most_im_five$names) %>% summarise_all(mean) %>% reshape2::melt(variable.name=c('varname'), value.name = c('cluster_mean')) 

# Get singular values of most important features for representative time series
repr_val <- all_data_labelled %>% filter(cls_center==1&cls_label == j-1) %>% select(most_im_five$names) %>% melt(variable.name=c('varname'), value.name = c('represent_TSfeature')) 


# Join values together
means_comp<-all_vals %>% inner_join(cls_vals, by=c('varname')) %>% inner_join(repr_val,by=c('varname')) #%>% mutate(repr = as_factor(c(0,0,1)))


# Make plot for each feature individually
out <- lapply(1:5,function(i){means_comp %>% 
    reshape2::melt(variable.name=c('group')) %>% 
    
    # Pick respective feature via filter
    filter(varname== most_im_five$names[i]) %>% 
    
    # Define column for who is representative
    mutate(representative=as_factor(c(F,F,T))) %>% 
    
    # Make Plot
    ggplot(aes(value,representative))+
    geom_line(aes(group=representative))+
    geom_point(aes(color=group, size = 5))+
    theme(axis.title.y = element_,
          axis.text.y=element_text(size=8),
          axis.text.x=element_text(size=8), 
          text = element_text(size=8), 
          legend.position = "none",
          )+
    # Title for orientation based on cls and varname
    ggtitle(paste(gsub("_", ".", most_im_five$names[i])))})
    #scale_y_discrete(labels=c('Averages', 'Representative'))

return(out)})





```

```{r}
grid.arrange(all_plts[[1]][[1]], all_plts[[1]][[2]], all_plts[[1]][[3]], ncol=3)
```


```{r}
library(gtable)
grid.arrange(ggplotGrob(all_plts[[1]][[1]]),ggplotGrob(all_plts[[1]][2]),ggplotGrob(all_plts[[1]][3]))

```
```{r}
library(gtable)
#g2 <- ggplotGrob(ggplotGrob(all_plts[[1]][[1]]))
#g3 <- ggplotGrob(ggplotGrob(all_plts[[1]][[2]]))
g <- rbind(all_plts[[1]][[1]], all_plts[[1]][[1]], size = "first")
#g$widths <- unit.pmax(g2$widths, g3$widths)
grid.newpage()
grid.draw(g)

```


### Collect lines in list
```{r,  fig.height=2, fig.width=15}
library(gridExtra)
n <- 5
nCol <- 5

plot_combis <- lapply(1:40,function(k){
do.call("grid.arrange", c(all_plts[[k]], ncol=nCol))})
```

### Plot entire 36 feature plots one one sheet
```{r,fig.height=100, fig.width=20}
n <- 40
nCol <- 1


do.call("grid.arrange", c(plot_combis, ncol=nCol))
```

```{r}

```

